---
title: "Shiny App - Analysis on ToothGrowth Data"
author: "Ruzaini Amiraa Roslan"
date: "9/18/2020"
output:
  slidy_presentation: default
---

## Introduction

- This presentation is created as the reproducible pitch for Coursera's "Developing Data Products" Week 4 course project.
- A Shiny app is created where the tooth length of guinea pigs is analyzed based on supplement type and dosage amount.
- The app can be found [here](), and the relevant codes and files can be found [here]().

## Data

- The dataset `ToothGrowth` is loaded from R `datasets` package.
- The variables are (based on the documentation of the data):
  - `len` - The tooth length of the guinea pigs
  - `supp` - Supplement type, whether it is ascorbic acid (coded as `VC`) or orange juice (coded as `OJ`)
  - `dose` - Dosage amount in milligrams per day
- A linea regression model is fitted using this data, and any new values are predicted using this model.

## Model Summary

```{r echo=TRUE}
data("ToothGrowth")
ToothGrowth$dose <- as.factor(ToothGrowth$dose)
model <- lm(len ~ ., data = ToothGrowth)
summary(model)
```

## Plots

```{r echo=FALSE}
library(ggplot2)

ggplot(ToothGrowth, aes(x = supp, y = len, fill = supp)) +
  geom_boxplot() +
  labs(x = "Supplement Type", y = "Tooth Length",
       title = "Tooth Length vs Supplement Type",
       fill = "Supp.Type")

ggplot(ToothGrowth, aes(x = dose, y = len, fill = dose)) +
  geom_boxplot() +
  labs(x = "Dosage", y = "Tooth Length",
       title = "Tooth Length vs Dosage",
       fill = "Dosage")
```

## Prediction for Supplement Type "OJ" and Dosage Amount of 1.0 mg/day

```{r echo=TRUE}
pred <- predict(model, newdata = data.frame(supp = "OJ", dose = as.factor(1.0)))
round(pred, 3)
```